Ontology Matching with word2vec

### 2016-03-07 Paper/Draft.tex
Restructured so that context if before problem

 \section{Problem}
 \subsection{Short Context}
 On the Semantic Web, ontologies are used to define and share knowledge. The term ontology will be properly defined later on, but for now it suffices to know that an ontology is a set of rules that determine what relations are allowed and required. On the semantic web, ontologies are the foundation for communication between agents.

 However, on the Semantic Web it is infeasible to use one single ontology, since the number of concepts it would have to contain is incredibly large. The larger an ontology the longer it takes to perform inference and searches on it, and thus to longer it takes to use it for communication. Therefore the semantic web will have separate ontologies for every domain. The downside of this approach is that when communication requires rules on multiple domains, which it often does, multiple ontologies need to be aligned or merged.
 \subsection{Problem}
 We have seen that when information from multiple domains need to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged. Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation. For example, the rule{\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and relationship \emph{being}.

 Lastly, there is the problem of 
 \subsection{Research questions}

@@

 The system uses an extensible framework which allows its users to add new modules to the system. This is very useful for research as it allows the researcher to compare different modules by swapping in just those modules in the framework. The module-swapping technique will also be used in this work, but more of that will be discussed in $Evaluation methods$.
 %http://disi.unitn.it/~p2p/RelatedWork/Matching/vldb2009-revised.pdf
 \section{Method}
 In this section, I will describe the method that I developed. Firstly, I will describe the general idea. In the second section, I will give a theoretical justification for why this method should work and how it works conceptually. After that I will describe the different ways that the input graphs can be used to train the word2vec model and create the alignment. 
 \subsection{Idea}
 As explained earlier, word2vec is a model that learns two things: implicitly it learns the semantic vector representation of words, and explicitly it learns to predict words from their context or vice versa. I will use both of these pieces of information in our alignment algorithm.
 The semantic representation will be used for finding nodes in the two ontology graphs that are similar, i.e. close in the vector space. This step is relatively straightforward if proper vector representations are found. However, this may be hard due to a number of problems which I have listed below.

>>>>

 \subsection{Short Context}
 On the Semantic Web, ontologies are used to define and share knowledge. The term ontology will be properly defined later on, but for now it suffices to know that an ontology is a set of rules that determine what relations are allowed and required. On the semantic web, ontologies are the foundation for communication between agents.

 However, on the Semantic Web it is infeasible to use one single ontology, since the number of concepts it would have to contain is incredibly large. The larger an ontology the longer it takes to perform inference and searches on it, and thus to longer it takes to use it for communication. Therefore the semantic web will have separate ontologies for every domain. The downside of this approach is that when communication requires rules on multiple domains, which it often does, multiple ontologies need to be aligned or merged.

@@

 The system uses an extensible framework which allows its users to add new modules to the system. This is very useful for research as it allows the researcher to compare different modules by swapping in just those modules in the framework. The module-swapping technique will also be used in this work, but more of that will be discussed in $Evaluation methods$.
 %http://disi.unitn.it/~p2p/RelatedWork/Matching/vldb2009-revised.pdf

 \section{Problem}

 \subsection{Problem}
 We have seen that when information from multiple domains need to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged. Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation. For example, the rule{\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and relationship \emph{being}.

 Lastly, there is the problem of different types of alignment relations. For example, one concept can be a \emph{part of} another concept, or an example of one. These different relations all require a different approach and come with their own sets of problems.

 In summary, ontology aligning is required for multi-domain communication but poses a number of problems that make it difficult for concepts, the building blocks of ontologies, to be matched.
 \subsection{Research questions}

 \section{Method}
 In this section, I will describe the method that I developed. Firstly, I will describe the general idea. In the second section, I will give a theoretical justification for why this method should work and how it works conceptually. After that I will describe the different ways that the input graphs can be used to train the word2vec model and create the alignment. 
 \subsection{Idea}
 As explained earlier, word2vec is a model that learns two things: implicitly it learns the semantic vector representation of words, and explicitly it learns to predict words from their context or vice versa. I will use both of these pieces of information in our alignment algorithm.
 The semantic representation will be used for finding nodes in the two ontology graphs that are similar, i.e. close in the vector space. This step is relatively straightforward if proper vector representations are found. However, this may be hard due to a number of problems which I have listed below.
